A pipeline to analyse time-course gene expression data

### 2020-07-04 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

The manuscript was last compile on 2020-06-24 09:03:07.

@@

\begin{verbatim}
## moanin_object on 209 samples containing the following information:
## 1) Meta data with 5 variables:
## [1] ""            "Group"       "Replicate"   "Timepoint"   "WeeklyGroup"
## 2) Basis matrix with 35 basis functions
## Basis matrix was constructed with the following formula
## ~Group + Group:splines::ns(Timepoint, df = degrees_of_freedom) + 0 
## Where degrees_of_freedom=6 
## To access these objects use:
##  <object_name>$degrees_of_freedom
##  <object_name>$basis
##  <object_name>$meta
##  <object_name>$formula
\end{verbatim}

>>>>

The manuscript was last compile on 2020-07-04 10:52:02.

@@

\begin{verbatim}
## moanin_model object on 209 samples containing the following information:
## 1) Meta data with 5 variables:
## [1] ""            "Group"       "Replicate"   "Timepoint"   "WeeklyGroup"
## 2) Basis matrix with 35 basis functions
## Basis matrix was constructed with the following formula
## ~Group + Group:splines::ns(Timepoint, df = degrees_of_freedom) + 0 
## Where degrees_of_freedom=6 
## To access these objects use:
##  <x_name>$degrees_of_freedom
##  <x_name>$basis
##  <x_name>$meta
##  <x_name>$formula
\end{verbatim}
